---
title: "LA1"
output:
  html_document: default
  pdf_document: default
date: '2022-06-25'
---
1.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
2.
```{r}
dataset<-read.csv("test_scores.csv")
max(dataset$school_setting)

```

3.Max of 

```{r}
max(dataset$school_setting)
```
4.
```{r}
search()
```
5.search() function in R Language is used to get the list of all the attached packages in the R search path. 
```{r}
head(dataset)
```
6.give all the top head
```{r}
tail(dataset)
```
7.all the details from tail
```{r}
head(dataset,10)
```
8.top ten data
```{r}
tail(dataset,10)
```
9.least 10 dataset
```{r}
str(dataset)
```
10.str() function in R Language is used for compactly displaying the internal structure of a R object. 
```{r}
names(dataset)
```
11.names() function in R Language is used to get or set the name of an Object.
```{r}
ls()
```
12.The ls() function in R is used to return a vector of character strings containing all the variables and functions that are defined in the current working directory in R programming. 
```{r}
x<-data.frame(dataset$school_setting)
```
```{r}
x
```
13.DISPLAYLING ONLY MENTIONED COLUMNS.
```{r}
max(dataset$school_setting)
```
14.maximum number of repetation of particular element.
```{r}
min(dataset$school_setting)
```
15.minimum number of repetation of particular element.
```{r}
median(dataset$school_type)
```
16.medain.
```{r}
mean(dataset$n_student)
```
17.mean
```{r}
mode(dataset$school_type)
```
18.mode finding.. maximum repeating.
```{r}
sort(dataset$n_student)
```
19.sorting in inceasing order.
```{r}
sort(dataset[1,])
```
20.sorting row 1.
```{r}
order(dataset$n_student)
```
21.ordering number of student column.
```{r}
rank(dataset$classroom)
```
22.ranking the classroom
```{r}
dimnames(dataset)
```
23.looks at column and row at the same time
```{r}
dimnames(dataset)
```
24.looks at column and row at the same time
```{r}
length(dataset$classroom)
```
25.length of classrom cloumn
```{r}
xyz=with(dataset,order(dataset$school_type,dataset$school_setting))
```
26....
```{r}
dataset.mat=as.matrix(dataset)
```
27.cpnverting the dataset into matrix
```{r}
dataset.mat
```
28.
```{r}
frame.list=as.list(dataset)
```
29.convert into list
```{r}
frame.list
```
30.standard deviation
```{r}
sd(dataset$n_student)
```
31.standard deviation without NA
```{r}
sd(dataset$n_student,na.rm = TRUE)
```
32.na-omit is used to strip out NA items
```{r}
length(na.omit(dataset$school_setting))
```
33.gives log
```{r}
log(dataset$n_student)
```
34.t()-rotates dataframe 
```{r}
t(dataset)
```
38. margin.table() command to get overall total
```{r}
margin.table(dataset$n_student)
```
39. display table data as proportion of total
```{r}
prop.table(dataset$n_student)
```
40.
```{r}
dataset[3,3]
```
42
```{r}
plot(dataset$student_id,dataset$n_student,xlab = "",ylab = "")
```
43.
```{r}
with(dataset,plot(student_id,n_student))
```
44.
```{r}
plot(dataset$posttest,dataset$n_student)
```
45.
```{r}
boxplot(dataset$pretest)
```
46.
```{r}
with(dataset,table(posttest,n_student))
```
47.
```{r}
summary(dataset)
```
48.
```{r}
rnorm(20,mean = 5,sd = 1)
```
49.
```{r}
addmargins(dataset,1,mean)
```
50.
```{r}
shapiro.test(dataset$n_student)
```
51.
```{r}
t(dataset)
```
52.
```{r}
row.names(dataset)
```
53.
```{r}
as.table(as.matrix(dataset))
```
54.
```{r}
class(dataset)
```
56.
```{r}
dataset.mat
```
57
```{r}
mean(dataset)
```
58.
```{r}
rank(dataset)
```
59.
```{r}
dataset[3,1:3]
```
60.stem()create stem and leaf plot
```{r}
stem(dataset$pretest)
```
61.
```{r}
matrix(x,ncol=5)
```
62.
```{r}
sample(dataset,size=5,replace = TRUE)
```
63.
```{r}
cov(dataset$n_student,dataset$posttest)
```
64.
```{r}
cor(dataset$n_student,dataset$posttest)
```
65.nothing is ploted only graph is produced
```{r}
plot(dataset$n_student,type = 'n')
```
66. pie
```{r}
dotchart(dataset$n_student)
```
67.
```{r}
barplot(dataset$posttest)
```
68. naming x and y axis
```{r}
barplot(dataset$n_student,xlab = 'a',ylab = 'b')
```
69. plot column of data.
```{r}
plot(dataset$n_student)

```
70. levels
```{r}
levels(dataset)
```
71. sacks arranges the value and pair index.
```{r}
mysatck=stack(dataset)
```
72.
```{r}
na.omit(stack(dataset))
```
73.
```{r}
matrix(x,ncol=5)
```
74.
```{r}
mysatck
```













