---
title: "LA_2"
output:
  html_document: default
  pdf_document: default
date: '2022-07-03'
---
1. First viewing the given dataset.
```{r}
dataset<-read.csv("test_scores.csv")
dataset
```
2. Scatter plot.
```{r}
library(ggplot2)
ggplot(dataset, aes(x = school_type, y = n_student)) +
geom_point()
```
3.creating a line graph.
```{r}
ggplot(dataset, aes(x = school_type, y = n_student)) +
geom_line()
```
3.Creating a Bar Graph
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_col()
```
creating a histogram
```{r}
ggplot(dataset, aes(y = n_student)) +
geom_histogram(binwidth = 4)
```
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_boxplot()
```
4.grouping graph together
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student, fill = school_setting)) +
geom_col(position = "dodge")
```
making bargraph of counts
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_bar()
```
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_col(width = 0.5)
```
```{r}
ggplot(dataset, aes(x = dataset$school_setting, y = dataset$n_student)) +
geom_col()
```
Cleveland Dot plot
```{r}
ggplot(dataset, aes(y = dataset$school_type, x = dataset$n_student)) +
geom_point()
```
Line graph
```{r}
ggplot(dataset, aes(y = dataset$school_setting, x = dataset$n_student)) +
geom_line()
```
Line graph with points
```{r}
ggplot(dataset, aes(y = dataset$n_student, x = dataset$n_student)) +
geom_line() +
geom_point()
```
Line graph with colour
```{r}
ggplot(dataset, aes(y = dataset$n_student, x = dataset$school_type)) +
geom_line(linetype =
"dashed"
, size =
1
, colour =
"blue"
)
```
graph with shaded area
```{r}
ggplot(dataset, aes(y = dataset$school_type, x = dataset$n_student)) +
geom_area()
```
Making histogram
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_histogram()
```
Making histogram with facet
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_histogram() +
facet_grid(school_setting ~ .)
```
Making density curve
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_density()
```
Making frequency plygon
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_freqpoly()
```
creating a violin plot
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_violin()
```
creating a violin plot with box plot
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_violin() + geom_boxplot(width =
.1
, fill =
"black"
, outlier.colour =
NA
)
```
creating a violin plot with smoothing
```{r}
ggplot(dataset, aes(x = dataset$school_type, y = dataset$n_student)) +
geom_violin(adjust=2
)
```
Making a dotplot
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_dotplot()
```
Making a dotplot with boxplot
```{r}
ggplot(dataset, aes(x = dataset$n_student)) +
geom_boxplot(outlier.colour =
NA
, width =
.4
) +
geom_dotplot()
```
